Incentivizing Exploration with Unbiased History

### 2018-11-02 model.tex
some comments
Minor edit.

We allow a much more permissive model, characterized by the following assumption:%
\footnote{In what follows, we make this assumption without further notice.}

>>>>

We allow a much more permissive model that allows each agent to form arbitrary reward estimates as long as they lie within some ``confidence range" of the sample average. Formally, the model is characterized by the following assumption (which we make without further notice).
